D3064R0: Bringing the Laws of Physics, Computer-System Constraints, and Compilers to Bear on the OOTA Problem

### 2024-01-18 ootavacuous.tex
Fix three-laws-of-physics typo s/earlier/later/
Reported-by: Dan Kelley <djk@meta.com>
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

These three laws of physics mean that if one thread loads the value
stored by some other thread, that load must have occurred earlier
in global time than did the store.
In other words, the reads-from relation is temporal in nature.

>>>>

These three laws of physics mean that if one thread loads the value
stored by some other thread, that load must have occurred later
in global time than did the store.
In other words, the reads-from relation is temporal in nature.
